HTW E1 Testing

### 2023-08-18 Analysis/e1_test.qmd
Individual diff plots for bayes fits.

@@

@@

```{r setup, include=FALSE}
source(here::here("Functions", "packages.R"))
test <- readRDS(here("data/e1_08-04-23.rds")) |> 
  filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)

e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())

@@

@@

e1_distBMM |> emmeans( ~condit + bandInt, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |>
  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
    ylab("Predicted Deviation") + xlab("Velocity Band")+
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(test$vb), 
                     limits = c(0, 1400)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

@@

cSamp <- e1_distBMM |> 
  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),epred = TRUE) |> 
  pairs() |> gather_emmeans_draws()  |>
  group_by(contrast, .draw,bandInt) |> summarise(value=mean(.value), n=n())

@@

e1_vxBMM |> emmeans( ~condit +bandInt, 
                       at=list(bandInt=c(100,350,600,800,1000,1200) )) |>
  gather_emmeans_draws() |>
  ggplot(aes(x=bandInt,y=.value,color=condit)) + 
  stat_lineribbon(aes(color=condit,fill=condit),alpha=.45,size=1,.width=c(.95)) + 
  ylab("Predicted Vx") + xlab("Velocity Band")

@@

```{r}
#| eval: false
indv_coefs <- coef(e1_vxBMM)$id |> 
  as_tibble(rownames="id") |> 
  select(id, starts_with("Est")) |>
  left_join(e1Sbjs, by=join_by(id) ) |> 
  # rank by Estimate.bandInt - within condit, higher is better
  group_by(condit) |> 
  mutate(rank = rank(desc(Estimate.bandInt)))

top_indv_coefs <- indv_coefs %>%
  filter(rank <= 1)

# Extract ids for top 10 subjects
top_ids <- top_indv_coefs$id
new_data=map_dfr(1, ~data.frame(unique(test[,c("id","condit","bandInt")]))) |> dplyr::arrange(id,bandInt) %>% filter(id %in% top_ids)
new_data$p <- predict(e1_vxBMM, newdata = new_data)

predictions <- t(posterior_predict(e1_vxBMM, newdata = new_data,ndraws=10))
new_data$prediction <- rowMeans(predictions)

# Generate predicted values
preds <- e1_vxBMM %>%
  epred_draws(newdata = new_data) %>%
  as_tibble() %>%
  left_join(newdata, by = "id")

# Plot
ggplot(preds, aes(x = bandInt, y = .epred, group = id, color = id)) +
  stat_lineribbon(alpha = 0.5) +
  labs(title = "Top 10 High Estimate.bandInt",
       x = "BandInt", y = "Predicted vx") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

@@

## Misc

{{< include "../Misc/alm_table.qmd" >}}

Here is a footnote reference,[^1] and another.[^2]

[^1]: Here is the footnote.
[^2]: Here's one with multiple blocks. Subsequent paragraphs are
    indented to show that they belong to the previous footnote.
    ```         
    { some.code }
    ```
Here is an inline note.[^3]

[^3]: Inlines notes are easier to write, since you don't have to pick an
    identifier and move down to type the note.

>>>>

```{r setup, include=FALSE}
source(here::here("Functions", "packages.R"))
test <- readRDS(here("data/e1_08-04-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

@@

{{< include ../Misc/bmm_table.qmd >}}

@@

@@

\begin{equation}
dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
\end{equation}

@@

e1_distBMM |> emmeans( ~condit + bandInt, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |>
  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
    ylab("Predicted Deviation") + xlab("Velocity Band")+
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(test$vb), 
                     limits = c(0, 1400)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
```

@@

cSamp <- e1_distBMM |> 
  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
          epred = TRUE, re_formula = NA) |> 
  pairs() |> gather_emmeans_draws()  |>
  group_by(contrast, .draw,bandInt) |> summarise(value=mean(.value), n=n())

@@

# e1_vxBMM |> emmeans( ~condit +bandInt, 
#                        at=list(bandInt=c(100,350,600,800,1000,1200) )) |>
#   gather_emmeans_draws() |>
#   ggplot(aes(x=bandInt,y=.value,color=condit)) + 
#   stat_lineribbon(aes(color=condit,fill=condit),alpha=.45,size=1,.width=c(.95)) + 
#   ylab("Predicted Vx") + xlab("Velocity Band")

@@

```{r}
#| label: fig-e1-indv-slopes
#| fig-cap: Subset of Varied and Constant Participants with the largest estimated slope values. Red lines represent the best fitting line for each participant, gray lines are 100 random samples from the posterior distribution. Colored points and intervals at each band represent the empirical median and 95% HDI. 
#| fig-height: 11

nTop <- 4

new_data_grid=map_dfr(1, ~data.frame(unique(test[,c("id","condit","bandInt")]))) |> 
  dplyr::arrange(id,bandInt) |> 
  mutate(condit_dummy = ifelse(condit == "Varied", 1, 0))

indv_coefs <- coef(e1_vxBMM)$id |> 
  as_tibble(rownames="id") |> 
  select(id, starts_with("Est")) |>
  left_join(e1Sbjs, by=join_by(id) ) |> 
  group_by(condit) |> 
  mutate(rank = rank(desc(Estimate.bandInt)),
         intErrorRank=rank((Est.Error.Intercept)),
         bandErrorRank=rank((Est.Error.bandInt)),
         nCond = n()) |> arrange(intErrorRank)

random_effects <- e1_vxBMM |> 
  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 500) |> 
  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
  mutate(id = factor(id,levels=levels(test$id))) |> 
  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)

fixed_effects <- e1_vxBMM |> 
  spread_draws(`^b_.*`,regex=TRUE) |> arrange(.chain,.draw,.iteration)

combined_df <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt) |>
  right_join(new_data_grid, by = join_by("id"),relationship="many-to-many") |> 
  mutate(
    fixed_effects = b_Intercept +
      (bandInt * b_bandInt) +
      condit_dummy * b_conditVaried + 
      (bandInt * condit_dummy) * `b_conditVaried:bandInt` ,  # Note: Replace : with correct operator
    random_effects = Intercept + bandInt_RF,  # Assuming random effects for intercept and bandInt
    estimate = fixed_effects + random_effects
  )

combined_df |> 
  filter(id %in% (indv_coefs |> filter(rank<=nTop) |> pull(id)) )  |> 
  group_by(id, bandInt) |>
  sample_n(10) |>
  ggplot(aes(x=bandInt,y=estimate)) + 
  geom_abline(aes(intercept=Intercept+b_Intercept, slope=bandInt_RF+b_bandInt), color="grey50", alpha=.2) +
  geom_abline(data=indv_coefs |> 
                filter(id %in% (indv_coefs |> filter(rank<=nTop) |> pull(id))),aes(intercept=Estimate.Intercept,slope=Estimate.bandInt),color="red") +
  stat_pointinterval(data=test |> filter(id %in% (indv_coefs |> filter(rank<=nTop) |> pull(id))), aes(x=bandInt,y=vx, color=vb)) +
  facet_nested_wrap(vars(condit,id),ncol = 2) +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(test$vb), 
                     limits = c(0, 1400)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +  ylab("X Velocity") + xlab("Band")

@@
